---
title: "Infant Touchscreen Use and Sleep Problems"
author: "Jessica Scarborough"
date: "5/7/2017"
output:
  html_document:
    theme: journal
    toc: true
    toc_depth: 4
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(truncnorm)
```

# Report Description

This report examines data simulation, exporation, and modeling analysis. The exploration portion of the project utilizes data visualization and MANOVA analysis. Modeling will begin with simple regression, and then move to multivariate multiple regression, ending with path analysis. 

**Predictor variables:**

* Age
* Gender
* Background TV
* Touchscreen use
* Night-time sleep duration
* Daytime sleep duration
* Average number of night awakenings
* Sleep onset

**Outcome variables:**

* Night-time sleep duration
* Daytime sleep duration
* Sleep onset
* Average number of night awakenings

# Data Simulation

**Count variables:**
```{r}
total.n <- 715

total.n.6_11 <- 134
total.n.12_18 <- 215
total.n.19_25 <- 179
total.n.26_36 <- 187

# N values for each age group in touchscreen use feature
screen.n.6_11 <- 123
screen.n.12_18 <- 194
screen.n.19_25 <- 145
screen.n.26_36 <- 151

# N values for each age group in background tv feature
tv.n.6_11 <- 123
tv.n.12_18 <- 194
tv.n.19_25 <- 145
tv.n.26_36 <- 151

```

**Touchscreen Variables:**
```{r}
screen.mean.6_11 <- 8.53
screen.mean.12_18 <- 18.80
screen.mean.19_25 <- 25.18
screen.mean.26_36 <- 44.11

screen.sd.6_11 <- 15.54
screen.sd.12_18 <- 36.83
screen.sd.19_25 <- 37.46
screen.sd.26_36 <- 47.75
```

##Age

I chose to simulate the age data with uniform distribution instead of rnorm, because there's no mention of normal distribution of age in the article. Additionally, normal distribution insinuates that there are very few samples on the lower and upper limits of each age group. This is not indicated in the paper. This makes uniform distribution a better option. 

```{r}
age.6_11 <- runif(n=total.n.6_11, min = 6, max = 11.9)
sd(age.6_11)
# sim sd: ~ 1.7
# original sd: 1.82
age.12_18 <- runif(n=total.n.12_18, min = 12, max = 18.9)
sd(age.12_18)
# sim sd: ~ 2.0
# original sd: 2.19

age.19_25 <- runif(n=total.n.19_25, min = 18, max = 25.9)
sd(age.19_25)
# sim sd: ~ 2.4
# original sd: 2.07

age.26_36 <- rnorm(n=total.n.26_36, mean=30.64, sd=3.07)
age.26_36 <- runif(n=total.n.26_36, min = 26, max = 36.9)
sd(age.26_36)
# sim sd: ~ 3.1
# original sd: 3.07


age <- c(age.6_11, age.12_18, age.19_25, age.26_36)
sd(age)
# sim sd: ~ 8.6
# original sd: 8.26

hist(age)
hist(age.6_11)
hist(age.12_18)
hist(age.19_25)
hist(age.26_36)

```

##Touchscreen Use
```{r}
# set.seed(0)

screen.6_11 <- (0.7)* rnorm(n=total.n.6_11, mean=(screen.mean.6_11-2.5), sd=screen.sd.6_11) + 
                (0.3)* rnorm(n=total.n.6_11, mean=3, sd=5)
screen.6_11 <- replace(screen.6_11, screen.6_11<0, 0)
screen.6_11[sample(1:length(screen.6_11), 
                   size = (total.n.6_11-screen.n.6_11), replace = FALSE)] <- NA
hist(screen.6_11)
sd(screen.6_11, na.rm = TRUE)
mean(screen.6_11, na.rm = TRUE)
# Sim mean typically hovers between 6.5-8.5
# Original mean: 7.53

# set.seed(0)
screen.12_18 <- (0.7)* rnorm(n=total.n.12_18, mean=(screen.mean.12_18-4), sd=screen.sd.12_18) + 
  (0.3)* rnorm(n=total.n.12_18, mean=10, sd=10)
screen.12_18 <- replace(screen.12_18, screen.12_18<0, 0)
screen.12_18[sample(1:length(screen.12_18), 
                    size = (total.n.12_18-screen.n.12_18), replace = FALSE)] <- NA
hist(screen.12_18)
sd(screen.12_18, na.rm = TRUE)
mean(screen.12_18, na.rm = TRUE)
# Sim mean typically hovers between 17-19.5
# Original mean: 18.8

# set.seed(0)
screen.19_25 <- (0.7)* rnorm(n=total.n.19_25, mean=(screen.mean.19_25-7), sd=screen.sd.19_25) + 
  (0.3)* rnorm(n=total.n.19_25, mean=15, sd=10)
screen.19_25 <- rnorm(n=total.n.19_25, mean=(25.18-7), sd=37.46)
screen.19_25 <- replace(screen.19_25, screen.19_25<0, 0)
screen.19_25[sample(1:length(screen.19_25), 
                    size = (total.n.19_25-screen.n.19_25), replace = FALSE)] <- NA
hist(screen.19_25)
sd(screen.19_25, na.rm = TRUE)
mean(screen.19_25, na.rm = TRUE)
# Final mean typically hovers between 24-28
# Original mean: 25.18

# set.seed(0)
screen.26_36 <- (0.7)* rnorm(n=total.n.26_36, mean=(screen.mean.26_36), sd=screen.sd.26_36) + 
  (0.3)* rnorm(n=total.n.26_36, mean=40, sd=10)
screen.26_36 <- replace(screen.26_36, screen.26_36<0, 0)
screen.26_36[sample(1:length(screen.26_36), 
                    size = (total.n.26_36-screen.n.26_36), replace = FALSE)] <- NA
hist(screen.26_36)
sd(screen.26_36, na.rm = TRUE)
mean(screen.26_36, na.rm = TRUE)
# Final mean typically hovers between 41-48
# Original mean: 44.11

hist(screen.6_11)
hist(screen.12_18)
hist(screen.19_25)
hist(screen.26_36)

screentime <- c(screen.6_11, screen.12_18, screen.19_25, screen.26_36)
hist(screentime)

# vectors with imputed data for future simulation needs
impute_screen.6_11 <- replace(screen.6_11, is.na(screen.6_11), 
                              mean(screen.6_11, na.rm=TRUE))
impute_screen.12_18 <- replace(screen.12_18, is.na(screen.12_18), 
                               mean(screen.12_18, na.rm=TRUE))
impute_screen.19_25 <- replace(screen.19_25, is.na(screen.19_25), 
                               mean(screen.19_25, na.rm=TRUE))
impute_screen.26_36 <- replace(screen.26_36, is.na(screen.26_36), 
                               mean(screen.26_36, na.rm=TRUE))

```
*For each age group*, the following steps were taken: 

1. Use rnorm to simulate data with the total n for the age group, discounting NA's for the time being, because we need the full indices in order to combine into a later df with age. 
2. Replace negative values with 0. Because this will raise the mean, I lowered the initial mean chosen with rnorm. 
3. Add in NA values based on the difference in the total n and the n for touchscreen use. 

**Note:** The final standard deviation values are not ideal using this procedure, but I decided that staying closer to the true mean (found in the original data set) was more important.


## Sex
```{r}
sex.6_11 <- rep(x = "Female", times = total.n.6_11)
sex.6_11[sample(1:length(sex.6_11), size=ceiling(total.n.6_11*0.5149), 
                replace = FALSE)] <- "Male"

sex.12_18 <- rep(x = "Female", times = total.n.12_18)
sex.12_18[sample(1:length(sex.12_18), size=ceiling(total.n.12_18*0.5302), 
                 replace = FALSE)] <- "Male"


sex.19_25 <- rep(x = "Female", times = total.n.19_25)
sex.19_25[sample(1:length(sex.19_25), size=ceiling(total.n.19_25*0.5587), 
                 replace = FALSE)] <- "Male"


sex.26_36 <- rep(x = "Female", times = total.n.26_36)
sex.26_36[sample(1:length(sex.26_36), size=ceiling(total.n.26_36*0.5134), 
               replace = FALSE)] <- "Male"

sex <- c(sex.6_11, sex.12_18, sex.19_25, sex.26_36)

```

*For each age group*, the following steps were taken: 

1. Use rep to create a vector with the total length N with "Female" as each value
2. Replace "Female" with "Male" based on the percetage of the age group that is male in the original data set


## Background TV
```{r}


# N values for each age group
tv.n.6_11 <- 123
tv.n.12_18 <- 194
tv.n.19_25 <- 145
tv.n.26_36 <- 151

# Screen values for each age group

tv_sd.6_11 <- 186.08
tv_sd.12_18 <- 172.70
tv_sd.19_25 <- 162.99
tv_sd.26_36 <-183.24

tv_mean.6_11 <- 209.72
tv_mean.12_18 <- 189.62
tv_mean.19_25 <- 187.00
tv_mean.26_36 <- 219.01

# Ratio balues for each age group
tv_screen_ratio.all <- 200.27/24.45
tv_screen_ratio.6_11 <- 209.72/8.53
tv_screen_ratio.12_18 <- 189.62/18.80
tv_screen_ratio.19_25 <- 187.00/25.18
tv_screen_ratio.26_36 <- 219.01/44.11


tv.6_11 <- (0.8)*(impute_screen.6_11 * tv_screen_ratio.6_11) + 
  (0.2)*(tv_mean.6_11 + rnorm(tv.n.6_11, sd=tv_sd.6_11))
tv.6_11[sample(1:length(tv.6_11), size=(total.n.6_11-tv.n.6_11), 
               replace = FALSE)] <- NA
tv.6_11 <- replace(tv.6_11, tv.6_11<0, 0)
mean(tv.6_11, na.rm=TRUE)


tv.12_18 <- (0.8)*(impute_screen.12_18 * tv_screen_ratio.12_18) + 
  (0.2)*(tv_mean.12_18 + rnorm(tv.n.12_18, sd=tv_sd.12_18))
tv.12_18[sample(1:length(tv.12_18), size=(total.n.12_18-tv.n.12_18), 
                replace = FALSE)] <- NA
tv.12_18 <- replace(tv.12_18, tv.12_18<0, 0)
mean(tv.12_18, na.rm=TRUE)



tv.19_25 <- (0.8)*(impute_screen.19_25 * tv_screen_ratio.19_25) + 
  (0.2)*(tv_mean.19_25 + rnorm(tv.n.19_25, sd=tv_sd.19_25))
tv.19_25[sample(1:length(tv.19_25), size=(total.n.19_25-tv.n.19_25), 
                replace = FALSE)] <- NA
tv.19_25 <- replace(tv.19_25, tv.19_25<0, 0)
mean(tv.19_25, na.rm=TRUE)



tv.26_36 <- (0.8)*(impute_screen.26_36 * tv_screen_ratio.26_36) + 
  (0.2)*(tv_mean.26_36 + rnorm(tv.n.26_36, sd=tv_sd.26_36))
tv.26_36[sample(1:length(tv.26_36), size=(total.n.26_36-tv.n.26_36), 
                replace = FALSE)] <- NA
tv.26_36 <- replace(tv.26_36, tv.26_36<0, 0)
mean(tv.26_36, na.rm=TRUE)


```

*For each age group*, the following steps were taken: 

1. Weighted values for each TV sample were created using:
- (0.8 weight) Ratio of mean background TV and mean touchscreen use * the touchscreen use vector (with imputed mean data where there were previously NAs)
- (0.2 weight) Mean TV + random noise
2. Negative values were set to 0
-This was beneficial to the final mean values, so the original values were not altered as was seen when this step was taken with touchscreen use
3. NAs were added based on difference in n for this feature and overall

**Note:** It would be possible to simulate this data in the manner used to simulate the screen time data, but I hypothesize that children that are more likely to use touchscreens are also more likely to be exposed to background TV. This is not stated in the article, but is an assumption I am making. If this was not my assumption, then I could simulate this data independent of the touchscreen values, just replicating the mean and SD for each age group

## Night-time sleep duration
```{r}


# Overall values for each age group
ntsleep.n.6_11 <- 116
ntsleep.n.12_18 <- 176
ntsleep.n.19_25 <- 132
ntsleep.n.26_36 <- 130

ntsleep.sd.6_11 <- 64.81
ntsleep.sd.12_18 <- 50.13
ntsleep.sd.19_25 <- 60.12
ntsleep.sd.26_36 <-61.81

ntsleep.mean.6_11 <- 637.24
ntsleep.mean.12_18 <- 647.24
ntsleep.mean.19_25 <- 651.25
ntsleep.mean.26_36 <- 643.21


# Ratio values for each age group
ntsleep_screen_ratio.6_11 <- ntsleep.mean.6_11/screen.mean.6_11
ntsleep_screen_ratio.12_18 <- ntsleep.mean.12_18/screen.mean.12_18
ntsleep_screen_ratio.19_25 <- ntsleep.mean.19_25/screen.mean.19_25
ntsleep_screen_ratio.26_36 <- ntsleep.mean.26_36/screen.mean.26_36

ntsleep.6_11 <- rtruncnorm(n=total.n.6_11, a=(ntsleep.mean.6_11-ntsleep.sd.6_11*2), 
                            b=(ntsleep.mean.6_11+ntsleep.sd.6_11*3),
                            mean=ntsleep.mean.6_11+30,
                            sd=ntsleep.sd.6_11) - 
                0.05*(impute_screen.6_11 * ntsleep_screen_ratio.6_11)
ntsleep.6_11[sample(1:length(ntsleep.6_11), size=(total.n.6_11-ntsleep.n.6_11), 
               replace = FALSE)] <- NA
hist(ntsleep.6_11)
mean(ntsleep.6_11, na.rm=TRUE)
# Sim mean hovers around: 633-644
# Original mean: 637.24

ntsleep.12_18 <- rtruncnorm(n=total.n.12_18, a=(ntsleep.mean.12_18-ntsleep.sd.12_18*2), 
                           b=(ntsleep.mean.12_18+ntsleep.sd.12_18*3),
                           mean=ntsleep.mean.12_18+35,
                           sd=ntsleep.sd.12_18) - 
                0.05*(impute_screen.12_18 * ntsleep_screen_ratio.12_18)
ntsleep.12_18[sample(1:length(ntsleep.12_18), size=(total.n.12_18-ntsleep.n.12_18), 
                    replace = FALSE)] <- NA
hist(ntsleep.12_18)
mean(ntsleep.12_18, na.rm=TRUE)
# Sim mean hovers around: 644-652
# Original mean: 647.24


ntsleep.19_25 <- rtruncnorm(n=total.n.19_25, a=(ntsleep.mean.19_25-ntsleep.sd.19_25*2), 
                            b=(ntsleep.mean.19_25+ntsleep.sd.19_25*3),
                            mean=ntsleep.mean.19_25+35,
                            sd=ntsleep.sd.19_25) - 
                0.05*(impute_screen.19_25 * ntsleep_screen_ratio.19_25)
ntsleep.19_25[sample(1:length(ntsleep.19_25), size=(total.n.19_25-ntsleep.n.19_25), 
                     replace = FALSE)] <- NA
hist(ntsleep.19_25)
mean(ntsleep.19_25, na.rm=TRUE)
# Sim mean hovers between: 648-654
# Original mean: 651.25

ntsleep.26_36 <- rtruncnorm(n=total.n.26_36, a=(ntsleep.mean.26_36-ntsleep.sd.26_36*2), 
                            b=(ntsleep.mean.26_36+ntsleep.sd.26_36*3),
                            mean=ntsleep.mean.26_36+36,
                            sd=ntsleep.sd.26_36) - 
  0.05*(impute_screen.26_36 * ntsleep_screen_ratio.26_36)
ntsleep.26_36[sample(1:length(ntsleep.26_36), size=(total.n.26_36-ntsleep.n.26_36), 
                     replace = FALSE)] <- NA
hist(ntsleep.26_36)
mean(ntsleep.26_36, na.rm=TRUE)
# Sim mean hovers around: 641-649
# Original mean: 643.21


ntsleep <- c(ntsleep.6_11, ntsleep.12_18, ntsleep.19_25, ntsleep.26_36)
hist(ntsleep)


```
*For each age group*, the following steps were taken: 

1. Weighted values for each night-time sleep duration sample were created by first creating a truncated normal distribution with a slightly higher mean than the original. 
2. A formula was used to create a value (in minutes) that was higher for samples with more touchscreen time. This value was multiplied by 0.05 and subtracted from the sample. It was only minimally influential, because the correlation between touchscreen and nighttime sleep was only -0.29. This shows that there is some correlation, but it is not particularly strong, so I didn't want to over do it. 
    - Formula: (Age Group Nighttime Sleep Mean)/(Age Group Screen Use Mean) * (Sample Screen Use)
3. NAs were added based on difference in n for this feature and overall



## Daytime sleep duration

```{r}

# Overall values for each age group
daysleep.n.6_11 <- 116
daysleep.n.12_18 <- 176
daysleep.n.19_25 <- 132
daysleep.n.26_36 <- 130

daysleep_sd.6_11 <- 64.81
daysleep_sd.12_18 <- 50.13
daysleep_sd.19_25 <- 60.12
daysleep_sd.26_36 <-61.81

daysleep_mean.6_11 <- 637.24
daysleep_mean.12_18 <- 647.24
daysleep_mean.19_25 <- 651.25
daysleep_mean.26_36 <- 643.21


# Ratio values for each age group
daysleep_screen_ratio.6_11 <- daysleep_mean.6_11/screen.mean.6_11
daysleep_screen_ratio.12_18 <- daysleep_mean.12_18/screen.mean.12_18
daysleep_screen_ratio.19_25 <- daysleep_mean.19_25/screen.mean.19_25
daysleep_screen_ratio.26_36 <- daysleep_mean.26_36/screen.mean.26_36


daysleep.6_11 <- (0.8)*(impute_screen.6_11 * daysleep_screen_ratio.6_11) + 
  (0.2)*(daysleep_mean.6_11 + rnorm(daysleep.n.6_11, sd=daysleep_sd.6_11))
daysleep.6_11[sample(1:length(daysleep.6_11), size=(total.n.6_11-daysleep.n.6_11),
                    replace = FALSE)] <- NA
daysleep.6_11 <- replace(daysleep.6_11, daysleep.6_11<0, 0)
mean(daysleep.6_11, na.rm = TRUE)


daysleep.12_18 <- (0.8)*(impute_screen.12_18 * daysleep_screen_ratio.12_18) + 
  (0.2)*(daysleep_mean.12_18 + rnorm(daysleep.n.12_18, sd=daysleep_sd.12_18))
daysleep.12_18[sample(1:length(daysleep.12_18), size=(total.n.12_18-daysleep.n.12_18),
                     replace = FALSE)] <- NA
daysleep.12_18 <- replace(daysleep.12_18, daysleep.12_18<0, 0)
mean(daysleep.12_18, na.rm = TRUE)


daysleep.19_25 <- (0.8)*(impute_screen.19_25 * daysleep_screen_ratio.19_25) + 
  (0.2)*(daysleep_mean.19_25 + rnorm(daysleep.n.19_25, sd=daysleep_sd.19_25))
daysleep.19_25[sample(1:length(daysleep.19_25), size=(total.n.19_25-daysleep.n.19_25),
                     replace = FALSE)] <- NA
daysleep.19_25 <- replace(daysleep.19_25, daysleep.19_25<0, 0)
mean(daysleep.19_25, na.rm = TRUE)


daysleep.26_36 <- (0.8)*(impute_screen.26_36 * daysleep_screen_ratio.26_36) + 
  (0.2)*(daysleep_mean.26_36 + rnorm(daysleep.n.26_36, sd=daysleep_sd.26_36))
daysleep.26_36[sample(1:length(daysleep.26_36), size=(total.n.26_36-daysleep.n.26_36),
                     replace = FALSE)] <- NA
daysleep.26_36 <- replace(daysleep.26_36, daysleep.26_36<0, 0)
mean(daysleep.26_36, na.rm = TRUE)

daysleep <- c(daysleep.6_11, daysleep.12_18, daysleep.19_25, daysleep.26_36)


```
*For each age group*, the following steps were taken: 

1. Weighted values for each daytime sleep duration sample were created using:
- (0.8 weight) Ratio of mean daytime sleep duration and mean touchscreen use * the touchscreen use vector (with imputed mean data where there were previously NAs)
- (0.2 weight) Mean daytime sleep duration + random noise
2. Negative values were set to 0
-This was beneficial to the final mean values, so the original values were not altered as was seen when this step was taken with touchscreen use
3. NAs were added based on difference in n for this feature and overall


## Total Sleep
```{r}

totalsleep <- ntsleep+daysleep

```


## Average number of night awakenings
```{r}

# Overall values for each age group

wake.n.6_11 <- 116
wake.n.12_18 <- 177
wake.n.19_25 <- 133
wake.n.26_36 <- 130

wake_sd.6_11 <- 1.73
wake_sd.12_18 <- 1.33
wake_sd.19_25 <- 1.01
wake_sd.26_36 <- 0.81

wake_mean.6_11 <- 2
wake_mean.12_18 <- 1.29
wake_mean.19_25 <- 0.91
wake_mean.26_36 <- 0.58


# Ratio values for each age group
wake_screen_ratio.6_11 <- wake_mean.6_11/screen.mean.6_11
wake_screen_ratio.12_18 <- wake_mean.12_18/screen.mean.12_18
wake_screen_ratio.19_25 <- wake_mean.19_25/screen.mean.19_25
wake_screen_ratio.26_36 <- wake_mean.26_36/screen.mean.26_36


wake.6_11 <- ceiling((0.8)*(impute_screen.6_11 * wake_screen_ratio.6_11) + 
  (0.2)*(wake_mean.6_11 + rnorm(wake.n.6_11, sd=wake_sd.6_11)) - 0.55)
wake.6_11[sample(1:length(wake.6_11), size=(total.n.6_11-wake.n.6_11),
                     replace = FALSE)] <- NA
wake.6_11 <- replace(wake.6_11, wake.6_11<0, 0)
mean(wake.6_11, na.rm = TRUE)


wake.12_18 <- ceiling((0.8)*(impute_screen.12_18 * wake_screen_ratio.12_18) + 
  (0.2)*(wake_mean.12_18 + rnorm(wake.n.12_18, sd=wake_sd.12_18))-0.45)
wake.12_18[sample(1:length(wake.12_18), size=(total.n.12_18-wake.n.12_18),
                      replace = FALSE)] <- NA
wake.12_18 <- replace(wake.12_18, wake.12_18<0, 0)
mean(wake.12_18, na.rm = TRUE)


wake.19_25 <- floor((0.8)*(impute_screen.19_25 * wake_screen_ratio.19_25) + 
  (0.2)*(wake_mean.19_25 + rnorm(wake.n.19_25, sd=wake_sd.19_25)))
wake.19_25[sample(1:length(wake.19_25), size=(total.n.19_25-wake.n.19_25),
                      replace = FALSE)] <- NA
wake.19_25 <- replace(wake.19_25, wake.19_25<0, 0)
mean(wake.19_25, na.rm = TRUE)


wake.26_36 <- ceiling((0.8)*(impute_screen.26_36 * wake_screen_ratio.26_36) + 
  (0.2)*(wake_mean.26_36 + rnorm(wake.n.26_36, sd=wake_sd.26_36))+.3)
wake.26_36[sample(1:length(wake.26_36), size=(total.n.26_36-wake.n.26_36),
                      replace = FALSE)] <- NA
wake.26_36 <- replace(wake.26_36, wake.26_36<0, 0)
mean(wake.26_36, na.rm = TRUE)

wake <- c(wake.6_11, wake.12_18, wake.19_25, wake.26_36)

```
*For each age group*, the following steps were taken: 

1. Weighted values for each night-time sleep duration sample were created using:
  - (0.8 weight) Ratio of mean night-time sleep duration and mean touchscreen use * the touchscreen use vector (with imputed mean data where there were previously NAs)
  - (0.2 weight) Mean night-time sleep duration + random noise
  - The floor or ceiling function and an added value that was chosen based on what created a reasonable overall mean value
2. Negative values were set to 0
-This was beneficial to the final mean values, so the original values were not altered as was seen when this step was taken with touchscreen use
3. NAs were added based on difference in n for this feature and overall


## Sleep onset
```{r}

# Overall values for each age group
onset.n.6_11 <- 116
onset.n.12_18 <- 177
onset.n.19_25 <- 131
onset.n.26_36 <- 130

onset_sd.6_11 <- 23.69
onset_sd.12_18 <- 16.53
onset_sd.19_25 <- 16.97
onset_sd.26_36 <- 27.86

onset_mean.6_11 <- 22.80
onset_mean.12_18 <- 21.54
onset_mean.19_25 <- 22.22
onset_mean.26_36 <- 29.34


# Ratio values for each age group
onset_screen_ratio.6_11 <- onset_mean.6_11/screen.mean.6_11
onset_screen_ratio.12_18 <- onset_mean.12_18/screen.mean.12_18
onset_screen_ratio.19_25 <- onset_mean.19_25/screen.mean.19_25
onset_screen_ratio.26_36 <- onset_mean.26_36/screen.mean.26_36


onset.6_11 <- (0.8)*(impute_screen.6_11 * onset_screen_ratio.6_11) + 
  (0.2)*(onset_mean.6_11 + rnorm(onset.n.6_11, sd=onset_sd.6_11))
onset.6_11[sample(1:length(onset.6_11), size=(total.n.6_11-onset.n.6_11),
                     replace = FALSE)] <- NA
onset.6_11 <- replace(onset.6_11, onset.6_11<0, 0)
mean(onset.6_11, na.rm = TRUE)


onset.12_18 <- (0.8)*(impute_screen.12_18 * onset_screen_ratio.12_18) + 
  (0.2)*(onset_mean.12_18 + rnorm(onset.n.12_18, sd=onset_sd.12_18))
onset.12_18[sample(1:length(onset.12_18), size=(total.n.12_18-onset.n.12_18),
                      replace = FALSE)] <- NA
onset.12_18 <- replace(onset.12_18, onset.12_18<0, 0)
mean(onset.12_18, na.rm = TRUE)


onset.19_25 <- (0.8)*(impute_screen.19_25 * onset_screen_ratio.19_25) + 
  (0.2)*(onset_mean.19_25 + rnorm(onset.n.19_25, sd=onset_sd.19_25))
onset.19_25[sample(1:length(onset.19_25), size=(total.n.19_25-onset.n.19_25),
                      replace = FALSE)] <- NA
onset.19_25 <- replace(onset.19_25, onset.19_25<0, 0)
mean(onset.19_25, na.rm = TRUE)


onset.26_36 <- (0.8)*(impute_screen.26_36 * onset_screen_ratio.26_36) + 
  (0.2)*(onset_mean.26_36 + rnorm(onset.n.26_36, sd=onset_sd.26_36))
onset.26_36[sample(1:length(onset.26_36), size=(total.n.26_36-onset.n.26_36),
                      replace = FALSE)] <- NA
onset.26_36 <- replace(onset.26_36, onset.26_36<0, 0)
mean(onset.26_36, na.rm = TRUE)

onset <- c(onset.6_11, onset.12_18, onset.19_25, onset.26_36)

```
*For each age group*, the following steps were taken: 

1. Weighted values for each sleep onset sample were created using:
- (0.8 weight) Ratio of mean sleep onset and mean touchscreen use * the touchscreen use vector (with imputed mean data where there were previously NAs)
- (0.2 weight) Mean sleep onset + random noise
2. Negative values were set to 0
-This was beneficial to the final mean values, so the original values were not altered as was seen when this step was taken with touchscreen use
3. NAs were added based on difference in n for this feature and overall



# Data Exploration



# Modeling

## Basic Regression

## Multivariate Multiple Regression

## Path Analysis


# Appendix

